### 2021-08-14 doc/thesis/chapters/introduction.tex
text
outline

TODO

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FEEDBACK, Meeting 07-16-2021
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%formatting:
%- absätze überall gleich (mit oder ohne leerzeile)
%references:
%- hauptsache überall gleich (Fig.2.3 oder Sec.7.1 oder Eq.3 oder Chpt.4)
%- literature refs at the beginning of a chapter/section
%  like "this chapter is based on [1][4][5]."
%  or at the end of the last sentence like "...the end of this sentence. [7]"
%
%Allgemeiner Teil / Theorie:
% zusätzliches kapitel:
%   system design ansätze
%   - from algo to VHDL (book: vom algorithmus zur hardware)
%   - matlab to VHDL
%   - systementwuf richtung test driven design
%   --> design space exploration
%
%
% ganze Arbeit aufhängen an:
%   main objective: fit all the aspects (algorithm, impl, testing) into
%                   a single project
%                  --> design space exploration
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FEEDBACK, Meeting 07-29-2021
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% ## Absätze
%   -- hab jetzt alle MIT Leerzeile
%
% ## Outline?
%   -- 1-2 Sätze Zusammenfassung zu jedem Chapter
%
% ## TITEL ändern
%   -- design of an fm receiver at system level using different methods
%
%   -- different approaches designing an fm receiver at system level
%
%   -- without the "fm receiver" part?
%
% ## maximale Länge der Arbeit?
%
% ## PRÜFUNG
%   -- H.G. nicht da --> 2 Möglichkeiten:  1. Oktober
%                                          2. Zweitfach PFA (AMV?)
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO General
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% ## unify all graphs and diagrams
%       - all gray; use exact same gray tone; eliminate the yellow?
%
% ## unify all references (use format like in caption)
%       - Figure 7.10
%       - Chapter 7.3
%       - Section 7.8
%       - Program 3.5
%       - etc.
%
% ## check all abbreviation and where they are introduced the first time
%       - introduce only once, like "device under test (DUT)",
%         then use the abbreviation only
%
% ## unify highlighted text ("Betonungen")
%       - use 'asdf' or \textit{asdf}
%
%
%
%

>>>>

Chapter \ref{cha:SignalProcessingTheory} describes the signal processing theory that is required to demodulate an FM broadcast radio signal.
This includes an introduction to receiver types, the description of an FM signal generally and also specifically as it is used in FM audio broadcasting, as well as various general topics of signal processing.
Chapter \ref{cha:SystemDesignProcess} covers the topic of a certain system design process, as well as system design tools that specifically target FPGAs.
Chapter \ref{cha:HLS} is about high-level synthesis, which includes a general introduction to the state of the art, as well as a description of the workflow, inclusively the coding and testbench features and characteristics.
Chapter \ref{cha:SystemArchitectureAndConcept} describes the chosen system architecture and concept for the project.
The actual implementation, with a detailed explanation of some selected components, is covered in Chapter \ref{cha:Implementation}.
Chapter \ref{cha:DeploymentOnHardware} gives an overview of the required parts of development that are necessary to deploy the developed IPs on actual hardware.
The comparison and achieved results are covered in Chapter \ref{cha:ComparisonAndResults}.
Chapter \ref{cha:ConclusionAndProspect} concludes this thesis with a retrospective and gives an outlook of potential future extensions to the project.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FEEDBACK, Meeting 07-16-2021
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%formatting:
%- absätze überall gleich (mit oder ohne leerzeile)
%references:
%- hauptsache überall gleich (Fig.2.3 oder Sec.7.1 oder Eq.3 oder Chpt.4)
%- literature refs at the beginning of a chapter/section
%  like "this chapter is based on [1][4][5]."
%  or at the end of the last sentence like "...the end of this sentence. [7]"
%
%Allgemeiner Teil / Theorie:
% zusätzliches kapitel:
%   system design ansätze
%   - from algo to VHDL (book: vom algorithmus zur hardware)
%   - matlab to VHDL
%   - systementwuf richtung test driven design
%   --> design space exploration
%
%
% ganze Arbeit aufhängen an:
%   main objective: fit all the aspects (algorithm, impl, testing) into
%                   a single project
%                  --> design space exploration
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FEEDBACK, Meeting 07-29-2021
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% ## Absätze
%   -- hab jetzt alle MIT Leerzeile
%
% ## Outline?
%   -- 1-2 Sätze Zusammenfassung zu jedem Chapter
%
% ## TITEL ändern
%   -- design of an fm receiver at system level using different methods
%
%   -- different approaches designing an fm receiver at system level
%
%   -- without the "fm receiver" part?
%
% ## maximale Länge der Arbeit?
%
% ## PRÜFUNG
%   -- H.G. nicht da --> 2 Möglichkeiten:  1. Oktober
%                                          2. Zweitfach PFA (AMV?)
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO General
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% ## unify all graphs and diagrams
%       - all gray; use exact same gray tone; eliminate the yellow?
%
% ## unify all references (use format like in caption)
%       - Figure 7.10
%       - Chapter 7.3
%       - Section 7.8
%       - Program 3.5
%       - etc.
%
% ## check all abbreviations and where they are introduced the first time
%       - introduce only once, like "device under test (DUT)",
%         then use the abbreviation only
%
% ## unify highlighted text ("Betonungen")
%       - use 'asdf' or \textit{asdf}
%
% ## fix the usage of apastrophes everywhere...
%       - see https://englishlive.ef.com/de-de/blog/grammatik-und-vokabeln/englischen-apostroph/
%
%
